Overview

### 2021-05-29 deploy.Rmd
Bump version; update NEWS; ready for CRAN

Please note that one cannot deploy oolong test objects with *both* word and topic intrusion tests, i.e. those created using `witi()` online. If you need to do both tests, you need to deploy them as two seperate instances: one created using `wi()` and another created using `ti()`.

@@

You can then obtain a locked oolong object from the original oolong and the downloaded data file. `revert_oolong` will do verfications with the original oolong object to make sure no error and no cheating.

>>>>

Please note that one cannot deploy oolong test objects with *both* word and topic intrusion tests, i.e. those created using `witi()` online. If you need to do both tests, you need to deploy them as two separate instances: one created using `wi()` and another created using `ti()`.

@@

You can then obtain a locked oolong object from the original oolong and the downloaded data file. `revert_oolong` will do verifications with the original oolong object to make sure no error and no cheating.
